When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-08 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
started results part

The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at [github.com/ChScheffel/CAD](https://github.com/ChScheffel/CAD).

>>>>

The paradigm code as well as the R Markdown file used to analyze the data and write this document are available at [github.com/ChScheffel/CAD](https://github.com/ChScheffel/CAD).

# Results

Data was collected between the 16th of August 2022 and the 3rd of February 2023.
Of the $N=$ participants who filled out the online questionnaires, $n=$ came to the first lab session.
Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the *n*-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
Our final data set therefore included $N=$ participants.
